Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-03-31 abstract.tex
Starting on algorithm description

We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
This model is defined as a sequence of vertices and triangular facets defined by the vertices.
This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{example-image-golden}
    \caption{Triaxial Ellipsoid Triangular Shape Model~\label{fig:initial_ellipsoid}}
\end{figure}

@@

Compute angle between measurement and all vertices of shape

>>>>

We assume that the spacecraft contains an initial estimate for the shape of the asteroid.
This shape can be a coarse estimate computed from radar measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid, such as that shown in~\cref{fig:initial_ellipsoid} which represents the maximum axes for asteroid Castalia.
This model is defined as a sequence of vertices, \( \vb{v}_i\), in the asteroid fixed frame and triangular facets, \( f_i = \bracket{\vb{v}_1, \vb{v}_2, \vb{v}_3}\), which are defined by the three vertices making up the facet.
This shape model is a widely used format for defining three-dimensional shapes in computer applications and has become the standard method for representing asteroid shapes~\cite{neese2004}.
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{example-image-golden}
    \caption{Triaxial Ellipsoid Triangular Shape Model~\label{fig:initial_ellipsoid}}
\end{figure}

@@

Our algorithm applies a Bayesian framework to radially modify each vertex \( \vb{v}_i\) of the shape estimate based on measurement \( \vb{p}_i\). 
This approach alleviates much of complexity of incorporating new vertices or surface triangulation common in surface reconstruction methods~\cite{berg2008}.
This assumption means that the total number of vertices of the shape model is fixed.
However, additional detail, in the form of additional vertices, is possible by using standard mesh subdivision algorithms~\cite{orourke1998}.

The radial distance of each vertex is assumed to be distributed according to the Gaussian distribution
\begin{align*}
    \norm{\vb{v}_i} \sim \mathcal{N}(r_0, w_0^2)
\end{align*}
where \( r_0 \) is the initial estimate of the radial distance of vertex \( \vb{v}_i\) and \( w_0 \) is the initial variance, or confidence, in the radial distance.
The radial distance of each measurement \( \vb{p}_i\) is also assumed to be distributed according to the Gaussian distribution
\begin{align*}
    \norm{\vb{p}_i} \sim \mathcal{N}(r_{m,i}, w_{m,i}^2)
\end{align*}
where \( r_m = \norm{\vb{p}_i} \) defines the true radial distance of the surface vector measurement and \( w_m\) defines the variance of the measurement with respect to vertex \( \vb{v}_i\).

The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
\begin{align}
    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
\end{align}
The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
\begin{align}
    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
\end{align}
This approach relates the uncertainty of the measurement with the distance to a given vertex.
As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty.

From Bayes' theorem, the 
Compute angle between measurement and all vertices of shape
